Robust Clustering for Ad Hoc Cognitive Radio Network

### 2017-12-28 journal-draft/ettdoc_JG.tex
minor changes
delete the line about solvers

We next focus on a single CR cluster. 
A cluster $C$ is a set of secondary nodes in an area, and there is a set of common channels which are available to each node belonging to the cluster.
One of the nodes belonging to the cluster is furthermore the cluster head $h(C)$.
The cluster head is able to communicate with any cluster member directly.
%Our scheme enables the cluster heads to be selected in a distributed manner, and a cluster can only be formed only by these selected cluster head.
%C1-4
%$\text{Nb}(i)$ denotes node $i$'s neighborhood which consists of all its one hop neighbors.
%For any cluster member $i \in C$, $i \in \text{Nb} (h_C) $ holds.
The number of nodes belonging to $C$ is denoted by $|C|$.
When the cluster head of a cluster is $i$, we denote that cluster by $C(i)$.
$K(C)$ denotes the set of CCs of all nodes in cluster $C$, i.e. $ K(C) = \bigcap_{i\in C} K_i$.
%Clustering is performed periodically, because the secondary users are mobile and the primary users change their operation channels, thus the channel availability on secondary users changes accordingly.
Table~\ref{tab1} summarizes all parameters and their assumed relevance in our system model. 
The usage scope is also provided when they are not used throughout the paper.
\begin{table}[h!]
\caption{Notations}
\label{tab1}
\centering
\begin{tabular}{llr}
\toprule
Symbol & Description \\
\midrule
$\mathcal{N}$  & set of CR users in a CRN\\
$N$ & number of CR users in a CRN, $N=|\mathcal{N}|$\\
$\mathcal{K}$	& set of licensed channels\\
%$k(i)$ & the working channel of user $i$\\
$\text{Nb}(i)$ & the neighborhood of CR node $i$    \\
$C(i)$ & a cluster whose cluster head is $i$  \\
$K_i$   & the set of available channels at CR node $i$  \\
$K(C(i))$   & the set of available CCs of cluster $C(i)$ \\
%$h(C)$ & cluster head of a cluster $C$\\
$h(C)$ & the cluster head of a cluster C\\
%$\text{CH}$ & cluster head\\
%$\text{CH}$ & cluster head\\
$\delta$ & the desired cluster size\\
$S_i$ & a set of claiming clusters, each of which \\
& includes debatable node $i$ after phase I\\
$f(C)$ & the number of CCs of a cluster $C$ in the\\ 
& problem description (Sec.~\ref{problem})\\
% $\mathcal{G}$ & a collection of some possible clusters in $\mathcal{N}$\\
 $\mathcal{S}$ & the collection of all the possible clusters \\
 & in $\mathcal{N}$ (Sec.~\ref{centralized_solution})\\
 $M$ & the cardinality of $\mathcal{S}$ (Sec.~\ref{centralized_solution})\\
 $C_i$  & the $i$-th cluster in $\mathcal{S}$ (Sec.~\ref{centralized_solution})\\
 %$|C_i|$ & the size of the cluster $C_i$\\
 %$|K(C_i)|$ & the number of CCs of cluster $C_i$\\
 $p$ & the weight with respect to cluster's size (Sec.~\ref{centralized_solution}) \\
 $d_i$  & individual connectivity degree of CR node $i$\\
$g_i$  & neighborhood connectivity degree of CR node $i$\\
  $n$ & the number of debatable nodes\\
 $m$ & the number of claiming cluster heads\\
 $J$ & the new value of $d_i$ for the CR node after it\\
 & becomes a cluster member (Sec.~\ref{ross})\\
% $e$ & cost function in the formulated game (Sec.~\ref{clustering:phaseII:game})\\
\bottomrule
\end{tabular}
\end{table}

@@

\section{Centralized Solution for Robust Clustering}
\label{centralized_solution}
%XXXXXX%
%Di writes: The first paragraph has been revised based on the first batch of comments for the camera-ready version, but somehow get lost in the last version. I take some parts from your revision and keep some from my revision.
We now turn to algorithms that can solve the CRN robust clustering problem, despite its complexity. 
We initially consider a centralized solution for this problem.
Assuming some global knowledge of the CRN to be given at some point in the network, \ie the locations of primary users and their working channels, and the locations of secondary users and available channels on them, we can propose a centralized scheme.
We obtain the set of $\mathcal{S}$ which contains all the clusters which satisfy the definition of cluster in Section~\ref{sec:model}.
$\mathcal{S}$ is basically a powerset of $\mathcal{N}$, which nevertheless is restricted by connectivity and spectrum availability in the network.
With $|\mathcal{S}| = M$, there is $\mathcal{S}=\{C_1, C_2, \ldots, C_M\}$ \footnote{The subscript $i$ means the $i$-th cluster in $\mathcal{S}$.}.
Then the problem as defined in Definition~\ref{def_centralized_clustering} can be formulated as a binary linear programming problem and can be solved by many available solvers:
\begin{equation}
%\begin{aligned}
%     &\max\limits_{y_i, x_{ij}} && \Sigma_{j=1}^N\Sigma_{i=1}^M (y_i\cdot \frac{q_{ij}}{|C_i|} - y_i\cdot p(C_i)) \\
%     &\text{subject to}   && \Sigma_{i=1}^M x_{ij} = 1, \text{for}\,\,\forall j=1, \ldots, N \\
%   &&& \Sigma_{j=1}^N x_{ij} = |C_i|\cdot y_i,\, \text{for}\,\,\forall i=1, \ldots, M \\
%  % &&& \text{$x_{ij}$ and $w_i$ are binary variables.}\\
%   &&& i\in \{1,2, \cdots M\}, \hspace{0.3cm} j\in \{1,2,\cdots N\}
%%\notag
%\end{aligned}
\begin{aligned}
     &\max\limits_{x_i} && \Sigma_{i=1}^M (x_i\cdot |K(C_i)| - x_i\cdot p(||C_i|-\delta|)) \\
     &\text{subject to}   && \Sigma_{i=1}^M (x_i\cdot e_{ij}) = 1  \quad\text{for}\,\,\forall j\in\{1, \ldots, N\} \\
%\notag
\end{aligned}
\label{centralized_opt}
\end{equation}
$x_i, i\in \{1,2, \cdots M\}$ is a set of binary optimization variables.
Being either 1 or 0, $x_i$ denotes whether the $i$-th cluster $C_i$ in $\mathcal{S}$ is chosen or not.
$e_{ij}, i\in \{1,2, \cdots M\}$ and $j=\{1, \ldots, N\}$ is a set of constants which indicate whether the CR node $j$ resides in the cluster $C_i$, \ie $e_{ij}=1$ means node $j$ resides in the cluster $C_i$, $e_{ij}=0$ indicates $j$ doesn't belong to that cluster .

>>>>

We next focus on a single CR cluster. 
A cluster $C$ is a set of secondary nodes in an area, and there is a set of common channels which are available to each node belonging to the cluster.
One of the nodes belonging to the cluster is furthermore the cluster head $h(C)$.
The cluster head is able to communicate with any cluster member directly.
%Our scheme enables the cluster heads to be selected in a distributed manner, and a cluster can only be formed only by these selected cluster head.
%C1-4
%$\text{Nb}(i)$ denotes node $i$'s neighborhood which consists of all its one hop neighbors.
%For any cluster member $i \in C$, $i \in \text{Nb} (h_C) $ holds.
The number of nodes belonging to $C$ is denoted by $|C|$.
When the cluster head of a cluster is $i$, we denote that cluster by $C(i)$.
$K(C)$ denotes the set of CCs of all nodes in cluster $C$, i.e. $ K(C) = \bigcap_{i\in C} K_i$.
%Clustering is performed periodically, because the secondary users are mobile and the primary users change their operation channels, thus the channel availability on secondary users changes accordingly.
Table~\ref{tab1} summarizes all parameters and their assumed relevance in our system model. 
The locations of the first appearances are provided for some notations.
\begin{table}[h!]
\caption{Notations}
\label{tab1}
\centering
\begin{tabular}{llr}
\toprule
Symbol & Description \\
\midrule
$\mathcal{N}$  & set of CR users in a CRN\\
$N$ & number of CR users in a CRN, $N=|\mathcal{N}|$\\
$\mathcal{K}$	& set of licensed channels\\
%$k(i)$ & the working channel of user $i$\\
$\text{Nb}(i)$ & the neighborhood of CR node $i$    \\
$C(i)$ & a cluster whose cluster head is $i$  \\
$K_i$   & the set of available channels at CR node $i$  \\
$K(C(i))$   & the set of available CCs of cluster $C(i)$ \\
%$h(C)$ & cluster head of a cluster $C$\\
$h(C)$ & the cluster head of a cluster C\\
%$\text{CH}$ & cluster head\\
%$\text{CH}$ & cluster head\\
$\delta$ & the desired cluster size\\
$S_i$ & a set of claiming clusters, each of which \\
& includes debatable node $i$ after phase I\\
$f(C)$ & the number of CCs of a cluster $C$ in the\\ 
& problem description (Sec.~\ref{problem})\\
% $\mathcal{G}$ & a collection of some possible clusters in $\mathcal{N}$\\
 $\mathcal{S}$ & the collection of all the possible clusters \\
 & in $\mathcal{N}$ (Sec.~\ref{centralized_solution})\\
 $M$ & the cardinality of $\mathcal{S}$ (Sec.~\ref{centralized_solution})\\
 $C_i$  & the $i$-th cluster in $\mathcal{S}$ (Sec.~\ref{centralized_solution})\\
 %$|C_i|$ & the size of the cluster $C_i$\\
 %$|K(C_i)|$ & the number of CCs of cluster $C_i$\\
 $p$ & the weight with respect to cluster's size (Sec.~\ref{centralized_solution}) \\
 $d_i$  & individual connectivity degree of CR node $i$\\
$g_i$  & neighborhood connectivity degree of CR node $i$\\
  $n$ & the number of debatable nodes\\
 $m$ & the number of claiming cluster heads\\
 $J$ & the new value of $d_i$ for the CR node after it\\
 & becomes a cluster member (Sec.~\ref{ross})\\
% $e$ & cost function in the formulated game (Sec.~\ref{clustering:phaseII:game})\\
\bottomrule
\end{tabular}
\end{table}

@@

\section{Centralized Solution for Robust Clustering}
\label{centralized_solution}
%XXXXXX%
%Di writes: The first paragraph has been revised based on the first batch of comments for the camera-ready version, but somehow get lost in the last version. I take some parts from your revision and keep some from my revision.
We now turn to algorithms that can solve the CRN robust clustering problem, despite its complexity. 
We initially consider a centralized solution for this problem.
Assuming some global knowledge of the CRN to be given at some point in the network, \ie the locations of primary users and their working channels, and the locations of secondary users and available channels on them, we can propose a centralized scheme.
We obtain the set of $\mathcal{S}$ which contains all the clusters which satisfy the definition of cluster in Section~\ref{sec:model}.
$\mathcal{S}$ is basically a powerset of $\mathcal{N}$, which nevertheless is restricted by connectivity and spectrum availability in the network.
With $|\mathcal{S}| = M$, there is $\mathcal{S}=\{C_1, C_2, \ldots, C_M\}$ \footnote{The subscript $i$ means the $i$-th cluster in $\mathcal{S}$.}.
Then the problem as defined in Definition~\ref{def_centralized_clustering} can be formulated as a binary linear programming problem.
% and can be solved by many available solvers:
\begin{equation}
%\begin{aligned}
%     &\max\limits_{y_i, x_{ij}} && \Sigma_{j=1}^N\Sigma_{i=1}^M (y_i\cdot \frac{q_{ij}}{|C_i|} - y_i\cdot p(C_i)) \\
%     &\text{subject to}   && \Sigma_{i=1}^M x_{ij} = 1, \text{for}\,\,\forall j=1, \ldots, N \\
%   &&& \Sigma_{j=1}^N x_{ij} = |C_i|\cdot y_i,\, \text{for}\,\,\forall i=1, \ldots, M \\
%  % &&& \text{$x_{ij}$ and $w_i$ are binary variables.}\\
%   &&& i\in \{1,2, \cdots M\}, \hspace{0.3cm} j\in \{1,2,\cdots N\}
%%\notag
%\end{aligned}
\begin{aligned}
     &\max\limits_{x_i} && \Sigma_{i=1}^M (x_i\cdot |K(C_i)| - x_i\cdot p(||C_i|-\delta|)) \\
     &\text{subject to}   && \Sigma_{i=1}^M (x_i\cdot e_{ij}) = 1  \quad\text{for}\,\,\forall j\in\{1, \ldots, N\} \\
%\notag
\end{aligned}
\label{centralized_opt}
\end{equation}
$x_i, i\in \{1,2, \cdots M\}$ is a set of binary optimization variables.
Being either 1 or 0, $x_i$ denotes whether the $i$-th cluster $C_i$ in $\mathcal{S}$ is chosen or not.
$e_{ij}, i\in \{1,2, \cdots M\}$ and $j=\{1, \ldots, N\}$ is a set of constants which indicate whether the CR node $j$ resides in the cluster $C_i$, \ie $e_{ij}=1$ means node $j$ resides in the cluster $C_i$, $e_{ij}=0$ indicates $j$ doesn't belong to that cluster .
